% GitHub Repo and Documentation: https://github.com/celiobjunior/resume-template
% Copyright © 2025 Celio B Junior. All rights reserved.
% 
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%     http://www.apache.org/licenses/LICENSE-2.0
%
% This template follows best practices from README.md

% Beginning of the LaTeX document: defines document type and format
% a4paper = A4 size, 10pt = base font size
\documentclass[a4paper,10pt]{article}

% --- PACKAGES: BASE / LANGUAGE ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

% --- PACKAGES: LAYOUT / TYPOGRAPHY ---
\usepackage{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{tabularx}

% --- PACKAGES: LINKS / BOOKMARKS ---
\usepackage{hyperref}
\usepackage{bookmark}
\usepackage{xurl}

% --- CONFIGURATION: MARGINS / SPACING ---
\geometry{top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm} % Page margins
\setcounter{secnumdepth}{0}                                  % Removes section numbering
\setlist[itemize]{
    leftmargin=0.75em, % List indentation
    itemsep=0.2em,     % Space between items
    topsep=0.25em,     % Space before/after lists
    parsep=0em,        % Space between paragraphs in the same item
    partopsep=0em      % Extra space at the start of a list
}

% Removes page numbers and headers for a clean resume layout
\pagestyle{empty}

% --- CONFIGURATION: METADATA / LINKS ---
\hypersetup{
    pdftitle={CV Pedro Franco}, % PDF title
    pdfauthor={Pedro Franco},   % PDF author
    colorlinks=true,            % Uses colored links without boxes
    linkcolor=black,            % Internal link color
    urlcolor=black,             % URL color
    citecolor=black,            % Citation color
    bookmarksdepth=2            % Sidebar: section and subsection
}

% --- CONFIGURATION: TITLES ---
\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}
[\titlerule\vspace{0.5ex}]
\titleformat{\subsection}
{\normalsize\bfseries}
{}
{0em}
{}
\titlespacing*{\subsection}{0pt}{0.35em}{0.15em}

% Macro for resume entries with PDF bookmarks
\newcounter{cventry}
\newcommand{\cventry}[4]{%
    \refstepcounter{cventry}%
    \phantomsection%
    \pdfbookmark[2]{#1}{cventry-\thecventry}%
    \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}p{0.68\textwidth} >{\raggedleft\arraybackslash}p{0.30\textwidth}@{}}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
    \end{tabularx}
}

% --- BEGIN DOCUMENT ---
\begin{document}

% --- HEADER ---
\begin{center}
    {\LARGE \textbf{Pedro Franco}}
    \\ [0.1cm]
    Mogi das Cruzes, SP
    {\textbullet}
    \href{tel:+5511996902133}{+55 11 99690-2133}
    {\textbullet}
    \href{mailto:amorimfranco1@gmail.com}{amorimfranco1@gmail.com}
    {\textbullet}
    \href{https://www.linkedin.com/in/pedro-franco-b40b3922b}{linkedin.com/in/pedro-franco-b40b3922b}
\end{center}

% --- SECTIONS ---

\section{Summary}
Systems Analysis and Development student at Fatec Mogi das Cruzes, currently in the 5th semester, with hands-on experience in mobile development using React Native, TypeScript, and Expo. Worked on end-to-end feature development, from interface implementation to REST API integration, including features with Google Places and Pagar.me. Professional experience in a software development environment, plus 2 semesters as an English teaching assistant. Fluent in English, with C1 proficiency certified by TOEIC.

% ------

\section{Experience}
    \cventry{Mestres da Web}{Mogi das Cruzes, SP}{Mobile Developer Intern}{May 2025 -- Apr. 2026}
        \begin{itemize}
            \item Developed mobile features with React Native, TypeScript, and Expo, working from interface implementation to REST API integration.
            \item Delivered complete features by converting layouts into functional screens and implementing business rules in mobile applications.
            \item Implemented Google Places integration for location features and interactive maps.
            \item Integrated Pagar.me for in-app payment flows.
        \end{itemize}

% ------

\section{Leadership and Teaching}
    \cventry{Fatec Mogi das Cruzes}{Mogi das Cruzes, SP}{English Teaching Assistant}{Aug. 2024 -- May 2025}
        \begin{itemize}
            \item Guided students during English tutoring sessions and study support over 2 semesters.
            \item Supported students' academic development through clear communication, content organization, and close follow-up.
        \end{itemize}

% ------

\section{Skills}
    \begin{itemize}
        \item \textbf{Languages:} TypeScript, JavaScript
        \item \textbf{Mobile:} React Native, Expo
        \item \textbf{Integrations:} REST APIs, Google Places, Pagar.me
        \item \textbf{Tools:} Git, GitHub, Postman
        \item \textbf{Languages Spoken:} Portuguese (native), English (fluent/C1)
        \item \textbf{Certification:} Test of English for International Communication (TOEIC)
    \end{itemize}

% ------

% !!!!!!!!!!!!!!!!!!!!!!
% Move this section to the top, after the header and before
% your experience, if you are looking for your first job or
% an internship. Otherwise, leave it as is.
% !!!!!!!!!!!!!!!!!!!!!!

\section{Education}
    \cventry{Fatec Mogi das Cruzes}{Mogi das Cruzes, SP}{Technologist Degree in Systems Analysis and Development}{Feb. 2024 -- Dec. 2026}

    \cventry{Unifesp -- Federal University of São Paulo}{São José dos Campos, SP}{Bachelor's Degree in Science and Technology --- completed through the 5th semester}{Mar. 2021 -- Jun. 2023}

    \cventry{Etec Presidente Vargas}{Mogi das Cruzes, SP}{Technical High School Program in Electronics}{Feb. 2018 -- Dec. 2020}

\end{document}
